Scikit-learn: machine learning without learning the machinery

### 2014-05-19 article.tex
Iter on paper

\paragraph{Supervised models: learning to predict}
%
The goal of supervised models is prediction. The corresponding estimators
have a

\paragraph{Model evaluation and parameter selection}
%
Model evaluation:
cross-validation: the concept, cross-val iterators, and cross\_val\_score

Problem of multiple metrics.

>>>>

\paragraph{Supervised models: learning to predict}
%
The goal of supervised models is prediction. The corresponding estimators
have a {\tt predict} method, that takes a data matrix $\mathbf{X}$ and
returns a predicted $\mathbf{y}$.

\paragraph{Model evaluation and parameter selection}
%
The data used to train a model can be used to measure the prediction
error, as it would be enable to distinguish noise from signal, and thus
overly optimistic. The correct way is to leave out \emph{test} data,
untouched during training. Often a \emph{cross-validation} scheme is
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides a complete framework for
cross-validation. Specific iterators are used to describe the subsets and
several functions and objects accept as arguments these iterators to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator.
